Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-16 README.Rmd
updated to do list

- Paper
  - Figure out discrepancies with old and new versions of the training data
  - Rerun the lime explanations with the finalized training data
  - Update all files in the submission folder
- Submission
  - Add Heike's ORCID ID
  - Not required but "Authors are requested to suggest at least one recommended reviewer"
  - Edit cover letter and upload
  - Enter the name of the Editor you are submitting to.
  - Edit dataset descriptions in README and add to the readme.txt document for submission
  - Upload the files for submission and submit
- Look into using renev

>>>>

- Paper
  - Adjust order of match and non-match in feature heat map
  - Train a random forest model on prepared training data (make sure to set a seed!) 
  - Make predictions on test data
  - Rerun all code in paper (check for changes in results)
  - Update text in paper to describe the random forest model process
  - Update all files in the submission folder
- Submission
  - Take photos of lime R package defaults with a data and save in figure-static for future reference and security
  - Determine the number of land comparisons in training data (in code file) and add to readme
  - Not required but "Authors are requested to suggest at least one recommended reviewer"
    - Matthias: does research related to visual explanations
    - Simon: exploratory data modeling
    - Pedersen: author of R lime package
  - Edit cover letter and upload
  - Edit dataset descriptions in README and add to the readme.txt document for submission
  - Upload the files for submission and submit
